\chapter{\iflanguage{ngerman}{Einleitung}{Introduction}}
\label{sec:Introduction}
The society for cancer estimates that every year 7,000 people in Germany are falling ill with a brain tumor. Many of them are in very deep and narrow spaces of the brain. Therefore the tumors cannot manually be removed by a surgeon because the risk to damage the brain is too high. If a surgery is not possible the patient has to do a radiation or chemo therapy. Both are taking a lot of time and energy from the patient. Nevertheless, it is not certain that such a therapy would heal the patient and the probability to damage other tissue is very high which leads to many secondary effects like hair loss. \\
Then there are diseases which are seen as incurable with manual surgeries like lymphoma. Manual tools can only help against the symptoms but not heal the patient. The same goes for retinal vein occlusion. \\
The third disadvantage of traditional surgeries is a long cut or big hole for inserting the surgeons tool is required which leads to a long recovery time and to a higher risk of infections.\\
The first step in improving surgeries was done with minimal invasive surgeries. The surgeon makes only one little cut and inserts the tools into the body and operates those over an endoscope. This step decreases the risk of infections and the recovery time of the patient.\\
The next step to a risk free surgery with low follow up effort and also in healing more diseases is the use of miniature robot systems. I will discuss the use of robotic systems for micro surgery in this work. I will discuss the application of the miniature robotic systems on the example of neurosurgery, Opthalmic and pregnancy help. The control of the robotic systems is the next point I will discuss. With the information won in these two chapter I will present a brief look into the future.
